%==========================================================
% Eser Menke - Curriculum Vitae
% Written in LaTeX. Compiles with pdfLaTeX.
%==========================================================
\documentclass[11pt,a4paper]{article}

% --- Packages ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[scaled=0.95]{helvet}   % clean sans-serif body font
\renewcommand{\familydefault}{\sfdefault}
\usepackage[margin=2cm]{geometry}
\usepackage[dvipsnames]{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}

% --- Colours ---
\definecolor{accent}{HTML}{2B6CB0}
\definecolor{soft}{HTML}{52606D}

% --- Links ---
\hypersetup{
  colorlinks=true,
  urlcolor=accent,
  linkcolor=accent,
  bookmarks=false
}

% --- Section formatting ---
\titleformat{\section}
  {\large\bfseries\color{accent}}
  {}{0em}{}[\vspace{2pt}\titlerule]
\titlespacing{\section}{0pt}{12pt}{6pt}

% Remove page numbers
\pagestyle{empty}

% --- Helper for entries ---
\newcommand{\entry}[4]{%
  \noindent\textbf{#1} \hfill \textcolor{soft}{#2}\\
  \textit{#3}\\[2pt]
  #4
}

\begin{document}

%========================== HEADER ==========================
\begin{center}
  {\Huge\bfseries Eser Menke}\\[6pt]
  {\large\color{soft} Software Engineering Student}\\[8pt]
  \small
  \href{mailto:esermenke1@gmail.com}{esermenke1@gmail.com} \quad\textbar\quad
  Berlin, Germany \\[2pt]
  \href{https://github.com/EserMenke}{github.com/EserMenke} \quad\textbar\quad
  \href{https://www.linkedin.com/in/eser-menke-710482403/}{linkedin.com/in/eser-menke} \quad\textbar\quad
  \href{https://esermenke.github.io}{esermenke.github.io}
\end{center}

\vspace{6pt}

%========================== PROFILE =========================
\section{Profile}
First-year software engineering student at Gisma University of Applied Sciences. I know the
basics of Python, C++, and web development, and I like building small projects to understand
how things work. I am looking for a working student position where I can keep learning and be
useful to the team.

%========================= EDUCATION ========================
\section{Education}

\noindent\textbf{Gisma University of Applied Sciences} \hfill \textcolor{soft}{2026 -- Present}\\
\textit{BSc Software Engineering, Berlin, Germany}\\[3pt]
Currently in my first year. Studying programming fundamentals, computer science basics, and
software development.

\vspace{8pt}

\noindent\textbf{High School Diploma} \hfill \textcolor{soft}{2023 -- 2024}

%========================== SKILLS ==========================
\section{Skills}
\begin{itemize}[leftmargin=1.2em, itemsep=2pt, topsep=2pt]
  \item \textbf{Programming:} Python, C++ (basics)
  \item \textbf{Web:} HTML, CSS
  \item \textbf{Tools:} Git, GitHub, LaTeX
\end{itemize}

%========================= LANGUAGES ========================
\section{Languages}
\begin{itemize}[leftmargin=1.2em, itemsep=2pt, topsep=2pt]
  \item \textbf{Turkish:} Native
  \item \textbf{English:} B2 -- C1
  \item \textbf{German:} Beginner (currently learning)
\end{itemize}

%========================= PROJECTS =========================
\section{Projects}

\noindent\textbf{Portfolio website} \hfill \textcolor{soft}{HTML, CSS}\\
A personal portfolio site built with HTML and CSS and hosted on GitHub Pages. My first time
building a full web page and publishing it online.

\vspace{6pt}

\noindent\textbf{Volume button orientation helper} \hfill \textcolor{soft}{C++}\\
A small C++ program for tablets that moves the volume up and down buttons depending on the
screen orientation, so they stay in a place that makes sense when the device is rotated.

\vspace{6pt}

\noindent\textbf{``Hello World'' web page} \hfill \textcolor{soft}{HTML}\\
My first HTML exercise. A single page that shows a message, where I started learning how a
web page is structured.

%========================= INTERESTS ========================
\section{Interests}
Technology, design, communication, and game development.

\end{document}
